\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]
\pdfgentounicode=1
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
%-------------------------------------------
\begin{document}
%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Om Magdum} \\ \vspace{1pt}
    \small Kolhapur, Maharashtra $|$ +91-7249797177 $|$ \href{mailto:magdumom.ml@gmail.com}{\underline{magdumom.ml@gmail.com}} $|$ 
    \href{https://github.com/ommagdum}{\underline{GitHub}} $|$
    \href{https://www.linkedin.com/in/om-ml-engg/}{\underline{LinkedIn}}
\end{center}
%-----------SUMMARY-----------
\section{Professional Summary}
\small{Final-year Computer Science graduate with hands-on experience in Java/Spring Boot microservices, event-driven systems, and full-stack development. Quick learner with a collaborative mindset, eager to contribute to enterprise-scale software engineering in a structured team environment. Skilled in PostgreSQL, Kafka, Docker, React, and OAuth2 --- AWS certified.}
%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java (17/21), Python 3.12, TypeScript, JavaScript (ES6+), SQL} \\
     \textbf{Backend}{: Spring Boot 3, Spring Security, Spring Data JPA, Spring Cloud, Apache Kafka} \\
     \textbf{Frontend}{: React 18, HTML5, CSS3, Tailwind CSS, Vite} \\
     \textbf{Databases}{: PostgreSQL, MongoDB, Redis, MySQL} \\
     \textbf{Cloud}{: AWS (Academy Cloud Foundations Certified)} \\
     \textbf{Security \& Architecture}{: Microservices, REST, OAuth2, OIDC, JWT, Keycloak, WebSockets (STOMP)} \\
     \textbf{Design Patterns}{: MVC, Repository, Factory, Event-Driven Architecture} \\
     \textbf{DevOps \& Testing}{: Docker, Maven, Git, JUnit 5, Mockito, JaCoCo, JMeter, ShedLock, Bucket4j, Resilience4j} \\
    }}
 \end{itemize}
%-----------EXPERIENCE-----------
\section{Work Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Software Engineering Intern (Part-time)}{Feb, 2026 -- May, 2026}
      {Vinayak IT Solutions}{Kolhapur, Maharashtra}
      \resumeItemListStart
        \resumeItem{Designed a multi-datasource PostgreSQL setup to isolate audit logs from core banking data, supporting high-reliability data pipelines and reducing query latency on transaction-heavy endpoints.}
        \resumeItem{Prevented database exhaustion on production REST APIs by implementing Bucket4j rate limiting (100 req/min), blocking 100\% of DDoS traffic.}
        \resumeItem{Prevented double-charges in a distributed banking environment by eliminating race conditions across concurrent scheduled triggers using Spring Boot 3 and ShedLock.}
        \resumeItem{Cut debugging time by 40\% and caught 7 critical pre-deployment bugs by bringing JaCoCo test coverage to 85\% via JUnit 5 and Mockito; collaborated with senior engineers on code reviews and technical documentation.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{MeetingMinutes AI $|$ Mega Project} $|$ \href{https://github.com/ommagdum/academic-meeting-minutes}{\underline{GitHub}}}{July, 2025 -- June, 2026}
          \resumeItemListStart
            \resumeItem{Built a containerized, cloud-ready Spring Boot + React + Flask microservices platform with MongoDB-backed persistence, handling 50 concurrent users at $<$200ms API response times.}
            \resumeItem{Integrated AI transcription pipeline (Whisper + Mistral 7B) via async, event-driven inter-service APIs, processing 60-minute audio in $<$7 minutes.}
          \resumeItemListEnd
          
      \resumeProjectHeading
          {\textbf{Event Ticket Platform} $|$ \href{https://github.com/ommagdum/tickets}{\underline{GitHub}}}{Nov 2025 -- Dec 2025}
          \resumeItemListStart
            \resumeItem{Secured user flows with Keycloak (OAuth2/OIDC) and custom Servlet Filters syncing identities to PostgreSQL, mirroring enterprise-grade customer identity management patterns.}
            \resumeItem{Dockerized the backend, Keycloak, and Adminer via Compose for consistent, reproducible environments across deployments.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{ML-Based Spam Email Detection Web App} $|$ \href{https://github.com/ommagdum/intelligent-spam-detection}{\underline{GitHub}}}{Jan 2025 -- May 2025}
          \resumeItemListStart
            \resumeItem{Architected a distributed full-stack application bridging a Spring Boot backend with a Python Flask service via asynchronous inter-service APIs to classify incoming email payloads.}
            \resumeItem{Deployed a TF-IDF + Naive Bayes model with live retraining, versioning, and rollback via dedicated REST endpoints.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Tatyasaheb Kore Institute of Engineering \& Technology}{Warananagar, Maharashtra}
      {Bachelor of Technology in Computer Science and Engineering --- CGPA: 7.55}{Oct 2022 -- June 2026}
  \resumeSubHeadingListEnd
%-----------CERTIFICATIONS-----------
\section{Certifications}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
      \textbf{AWS Academy Graduate --- Cloud Foundations} $|$ \href{https://www.credly.com/badges/6537fbfe-992b-4708-b442-c3e197cf2af0/public_url}{\underline{\emph{Amazon Web Services}}} \hfill Nov 2025 \\
      \textbf{Java Spring Framework 6 with Spring Boot 3} $|$ \href{https://www.udemy.com/certificate/UC-d846a318-218c-4b7d-8bee-7e0fbcb08073/}{\underline{\emph{Udemy}}} \hfill Mar 2025
    }}
  \end{itemize}
\end{document}